Developing a Visual Studio Code Language Support Extension for the Snail Programming Language

### 2023-06-05 paper.tex
feat: insert section outline

>>>>

\subsection{History of the Modern Integrated Development Environment}

\subsection{History of Modern Debugging Tools}

\subsection{What is Visual Studio Code?}

\section{Anatomy of a Visual Studio Code Extension}

\subsection{Directory Structure}

\subsection{Extension Contributions: The Extension Manifest}

\subsection{Extension Lifecycle: From Startup to Shutdown}

\subsection{Language Configuration}

\subsection{Rudimentary Autocompletion Through Snippets}

\subsection{Syntax Highlighting}

\section{Language Servers and the Language Server Protocol (LSP)}

\subsection{Theory}

\subsection{LSP in Snail Language Support}

\section{Debug Adapter Protocol}

\subsection{Theory}

\subsection{Debug Adapter Protocol in Snail Language Support}

\section{Good Practices in Software Development}

\subsection{Version Control}

\subsection{Documentation}

\section{Conclusions}

%== APPENDICES ==%
\newpage

\section{Appendices}

\appendix

\section{Title of Some File}\label{A}
